Transforming Trash as an Artistic Act

### 2016-01-08 chapter3_reduced.tex
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d

@@

\begin{singlespace}
\begin{quote}
The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way. In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism...

Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread. \citep{webster2011kurt}
\end{quote}
\end{singlespace}

@@

% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
\begin{singlespace}
\begin{quote}
The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin. \citep{carroll2011ruin}
\end{quote}
\end{singlespace}

@@

%
%
\section{Examples from contemporary artists}
In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed. First one is related with found objects. In this section focus will be shifted to the examples from contemporary artists.

@@

Prior to film Amélie, British artist Dick Jewell published a book in title of "Found Photos" in 1977. It is a collection of photobooth images that had been thrown away or torn up by the people in the photos. \cite{walker2010dick} comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine. They are scavenged by the artist from the photo booths of London. The reasons of why photos are rejected vary including technical problems like flash or posing time. On the other hand, some of them are very good condition, and it is a mystery that why they are rejected. Walker explains that the

\begin{singlespace}
\begin{quote}
gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving.
\end{quote}
\end{singlespace}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
  \caption{Michael Landy, Break Down}
  \label{fig:MichaelLandy_BreakDown}
\end{figure}

% TODO kendi işime taşıyacağım.
% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa, http://www.eloisacartonera.com.ar/ENGversion.html
%\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers. \quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]

@@

%
%
\section{The documentary \quotes{The Gleaners and I} by Agnès Varda}
"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000. The film features various kinds of gleaning. According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers". Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her filmmaking practice. Some people glean crops; the others discarded food, and Varda gleans images.

>>>>

% Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.

@@

\begin{quote}
The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way. In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism...

Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread. \citep{webster2011kurt}
\end{quote}

@@

% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
\begin{quote}
The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin. \citep{carroll2011ruin}
\end{quote}

@@

%
%
\section{Examples from Contemporary Artists}
In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed. First one is related with found objects. In this section focus will be shifted to the examples from contemporary artists.

@@

Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977. It is a collection of photobooth images that had been thrown away or torn up by the people in the photos. \cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine. They are scavenged by the artist from the photo booths of London. The reasons of why photos are rejected vary including technical problems like flash or posing time. On the other hand, some of them are very good condition, and it is a mystery that why they are rejected. Walker explains that the

\begin{quote}
gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving.
\end{quote}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin, 2014}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

% Landy'nin yaptığı bir çok iş aslında çöple ilgili olduğu savunulabilir. Hepsinin anlatmak mümkün olmasada bir diğer için sahip olduğu tüm eşyaları bozmasıyla ilgili. Daha önceden bahsettiğim geri dönüştürme tanımları ile ilgili olarak bu işi downcycling yöntemi arasında görülebilir.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
  \caption{Michael Landy, Break Down, 2001}
  \label{fig:MichaelLandy_BreakDown}
\end{figure}

% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa, http://www.eloisacartonera.com.ar/ENGversion.html
%\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers. \quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]

@@

% , as illustrated by the examples cited so far,

% Örnek sadece bunlarla sınırlı değil, daha bir çoğu sayılabilir, plastik poşetinde şiirselliğin yakalandığı american beauty filmi, kamusal alanı dönüştüren sanatçılar gibi.

%
%
\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000. The film features various kinds of gleaning. According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers". Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her filmmaking practice. Some people glean crops; the others discarded food, and Varda gleans images.
